On the number of tiles visited by a\\ line segment on a rectangular grid

### 2021-08-24 paper.tex
Wording in introduction

Given $a, b \in \mathbb R^+$, consider a grid on $\mathbb R^2$ formed by rectangular \emph{tiles} of width $a$ and height $b$. A line segment of length $\len \in \mathbb R^+$ is located on the plane with arbitrary position and orientation. The segment is said to \emph{visit} a tile if it intersects its interior.\footnote{
The definition uses the interior of the tile, excluding the border, to avoid uninteresting results such as a ``zero-length'' segment visiting (a vertex of) $4$ tiles.} This paper deals with the following problems:
\begin{itemize}
\item What is the maximum number of tiles that the segment can visit?
\item What length should a segment have to visit a given number of tiles?
\item What is the average number of tiles visited by a uniformly random segment of a given length? How often does the random segment visit the maximum number of tiles?
\end{itemize}

@@

The problem of how many tiles a \emph{random} segment of a given length visits is precisely defined as follows. By symmetry, one endpoint of the segment can be assumed to lie in a fixed, reference tile. The position of this endpoint is \emph{uniformly} distributed on the tile. The segment orientation has a \emph{uniform} distribution on the set of all possible directions, and is \emph{independent} of the endpoint position. As will be seen, solving the problem of how many tiles the segment visits on average also answers the inverse question (segment length to visit a given number of tiles on average). In addition, it is interesting to know the probability that the segment visits the maximum number of tiles.

>>>>

Given $a, b \in \mathbb R^+$, consider a grid on $\mathbb R^2$ formed by rectangular \emph{tiles} of width $a$ and height $b$. A line segment of length $\len \in \mathbb R^+$ is located on the plane with arbitrary position and orientation. The segment is said to \emph{visit} a tile if it intersects its interior.\footnote{
The definition uses the interior of the tile, excluding the border, to avoid uninteresting results such as a ``zero-length'' segment visiting (a vertex of) $4$ tiles.} This paper deals with the following problems:
\begin{itemize}
\item What is the maximum number of tiles that the segment can visit? Conversely, what length should a segment have to visit a given number of tiles?
\item What is the average number of tiles visited by a uniformly random segment of a given length? How often does the random segment visit the maximum number of tiles?
\end{itemize}

@@

The notion of a \emph{random} segment of a given length is precisely defined as follows. By symmetry, one endpoint of the segment can be assumed to lie in a fixed, reference tile. The position of this endpoint is \emph{uniformly} distributed on the tile. The segment orientation has a \emph{uniform} distribution on the set of all possible directions, and is \emph{independent} of the endpoint position. Solving the problem of how many tiles the segment visits on average, as will be seen, also answers the inverse question (segment length to visit a given number of tiles on average). In addition, a natural question is with that probability the segment visits the maximum number of tiles.
